Robust Quantum Optimal Control

### 2020-09-01 paper/paper.tex
all 3 figures

%% ABSTRACT
\begin{abstract}
  %% - 1 + 2 topic importance
  %% - 1 what I have done
  %% - few sentences about primary results
  The ability to engineer high fidelity operations on quantum processors in the presence of
  decoherence and systematic errors remains the primary challenge to achieving quantum advantage.
  Quantum optimal control (QOC) techniques have been developed to mitigate deleterious effects
  by manipulating the time-dependent parameters controlling the system. These techniques often
  target a single error channel and may be incompatible with experimental constraints. 
  In this work, we develop techniques to simultaneously mitigate
  longitudinal relaxation and pure dephasing in a framework that may impose arbitrary
  experimental constraints.
  Optimizing a gate set for a fluxonium qubit as an example, we achieve a factor of 4 increase in
  longitudinal relaxation times and outperform
  existing dynamic decoupling methods in mitigating pure dephasing, achieving
  high fidelity gates in the presence of parameter spreads up to $5\%$.
\end{abstract}

@@

(Outline) As an example, we study the quantum optimal control problem on
the fluxonium qubit presented in \cite{zhang2020universal}.
We describe experimentally realistic constraints and map them to
the trajectory optimization framework. Next, we
outline a method for making the optimization longitudinal
relaxation aware. We achieve a 4x decrease in longitudinal relaxation times
over the baseline gate set.
We present two methods for achieving robustness to pure dephasing
and compare them to existing dynamic decoupling methods. We find that
the methods we employ outperform dynamic decoupling, producing
high fidelity gates at system parameter spreads of $5\%$.

@@

%% F4.1
\begin{figure}[ht]
  \begin{subfigure}{\linewidth}
    \includegraphics[width=\linewidth]{assets/f1a.png}
  \end{subfigure}
  \begin{subfigure}{\linewidth}
    \includegraphics[width=\linewidth]{assets/f1b.png}
  \end{subfigure}
  \begin{subfigure}{\linewidth}
    \includegraphics[width=\linewidth]{assets/f1c.png}
  \end{subfigure}
  \caption{(a) $T_{1}$ optimized gates (orange) and analytic gates (blue). (b) Master equation simulation with $T_{1}$ dissipation
    for all gates, over the course of concatenated gate applications. (c) $T_{1}$ interpolation function used in optimization
    and the corresponding $T_{1}$ times for the average absolute amplitude of each gate.}
\end{figure}

@@

%% F5.1
\begin{figure}[ht]
  \begin{subfigure}{\linewidth}
    \label{fig:5.1:a}
    \includegraphics[width=\linewidth]{assets/f2a.png}
  \end{subfigure}

  \begin{subfigure}{\linewidth}
    \label{fig:5.1:b}
    \includegraphics[width=\linewidth]{assets/f2b.png}
  \end{subfigure}

@@

  \caption{\centering (a) $X/2$ gates constructed from the analytic, (2, 4)-point
    sampling, and (2, 3)-derivative robustness methods at a gate duration of $56.8 (ns)$.
    (b) Gate error as a function of qubit frequency detuning from the nominal frequency.
    (c) Average gate error at one standard deviation from the nominal qubit frequency as
    a function fo the gate duration.
  }
\end{figure}

%% F5.2
%% TODO: Make this figure.
\begin{figure}[ht]
  \includegraphics[width=\linewidth]{assets/t2_temp.jpg}
  \caption{Robustness to $T_{\phi}$-type noise for the
    the (2, 4)-point sampling method, (2\textsuperscript{nd}, 3\textsuperscript{rd})
    order derivative method, and B2CORPSE pulse for the $R_{x}(\pi/2)$ gate.}
\end{figure}

>>>>

%% ABSTRACT
\begin{abstract}
  %% - 1 + 2 topic importance
  %% - 1 what I have done
  %% - few sentences about primary results
  The ability to engineer high fidelity operations on quantum processors in the presence of
  decoherence and systematic errors remains the primary challenge requisite to achieving quantum advantage.
  Quantum optimal control (QOC) techniques have been developed to mitigate deleterious effects
  by manipulating the time-dependent parameters controlling the system. These techniques often
  target a single error channel and may be incompatible with experimental constraints. 
  In this work, we develop techniques to simultaneously mitigate
  longitudinal relaxation and pure dephasing in a framework that can handle arbitrary
  experimental constraints.
  Optimizing a gate set for a fluxonium qubit as an example, we achieve a factor of 4 increase in
  longitudinal relaxation times and outperform
  existing dynamic decoupling methods in mitigating pure dephasing due to flux noise, achieving
  high fidelity gates in the presence of parameter spreads up to $5\%$.
\end{abstract}

@@

(Outline) As an example, we study the quantum optimal control problem on
the fluxonium qubit presented in \cite{zhang2020universal}.
We describe experimentally realistic constraints and map them to
the trajectory optimization framework. Next, we
outline a method for making the optimization longitudinal
relaxation aware. We achieve a 4x increase in longitudinal relaxation times
over the baseline gate set.
We present two methods for achieving robustness to pure dephasing
and compare them to existing dynamic decoupling methods. We find that
the methods we employ outperform dynamic decoupling, producing
high fidelity gates at system parameter spreads of $5\%$.

@@

%% F1
\begin{figure}[ht]
  \begin{subfigure}{.49\linewidth}
    \includegraphics[width=\linewidth]{assets/f1a.png}
  \end{subfigure}\hfill%
  \begin{subfigure}{.49\linewidth}
    \includegraphics[width=\linewidth]{assets/f1b.png}
  \end{subfigure}
  \begin{subfigure}{\linewidth}
    \includegraphics[width=\linewidth]{assets/f1c.png}
  \end{subfigure}
  \caption{(a) $T_{1}$ optimized gates (orange) and analytic gates (blue). (b) Master equation simulation with $T_{1}$ dissipation
    for all gates, over the course of concatenated gate applications. (c) $T_{1}$ interpolation function used in optimization
    and the corresponding $T_{1}$ times for the average absolute amplitude of each gate.}
\end{figure}

@@

%% F2
\begin{figure}[ht]
  \begin{subfigure}{.49\linewidth}
    \label{fig:5.1:a}
    \includegraphics[width=\linewidth]{assets/f2a.png}
  \end{subfigure}%
  \begin{subfigure}{.49\linewidth}
    \label{fig:5.1:b}
    \includegraphics[width=\linewidth]{assets/f2b.png}
  \end{subfigure}

@@

  \caption{\centering (a) $X/2$ gates robust to qubit frequency offsets
    constructed using the analytic, (2, 4)-point
    sampling, and (2, 3)-derivative methods at a gate duration of $56.8 (ns)$.
    (b) Gate error as a function of qubit frequency detuning from the nominal frequency.
    (c) Average gate error at one standard deviation from the nominal qubit frequency as
    a function fo the gate duration.
  }
\end{figure}

%% F3
\begin{figure}[ht]
  \begin{subfigure}{.5\linewidth}
    \includegraphics[width=\linewidth]{assets/f3a.png}
  \end{subfigure}%
  \begin{subfigure}{.5\linewidth}
    \includegraphics[width=\linewidth]{assets/f3c.png}
  \end{subfigure}

  \begin{subfigure}{\linewidth}
    \includegraphics[width=\linewidth]{assets/f3b.png}
  \end{subfigure}

  \caption{\centering (a) $X/2$ gates robust to flux offsets constructed using the analytic,
    (2, 4)-point sampling, and (2, 3)-derivative methods at a gate duration
    of $56.8 (ns)$. (b) Mean gate error for 10 samples of 1/$f$ flux noise over 5000
    gate applications. (c) Stochastic 1/$f$ flux noise.}
\end{figure}
